---
title: "Immigration"
format: html
author: "Surya Fraser"
execute: 
  echo: false
---

```{r}
#| message: false
library(tidyverse) 
library(primer.data)
library(tidymodels)
library(broom)
library(marginaleffects)
```

$$
g(\mathbb{E}[Y \mid \mathbf{X}]) = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \cdots + \beta_p X_p
$$

$$
\widehat{\text{att\_end}} = 75.2 + 4.8 \cdot \text{treatment}
$$

```{r}
#| cache: true
fit_att <- linear_reg(engine = "lm") |> 
  fit(att_end ~ treatment, data = trains)
```

```{r}
library(gt)

# Tidy model output with confidence intervals
fit_att_tidy <- tidy(fit_att, conf.int = TRUE)

# Create a nice table using gt
fit_att_tidy |> 
  mutate(term = recode(term,
                       "(Intercept)" = "Intercept",
                       "treatment" = "Treatment")) |> 
  gt() |> 
  tab_header(
    title = "Linear Regression Coefficients",
    subtitle = "Model: att_end ~ treatment"
  ) |> 
  fmt_number(
    columns = where(is.numeric),
    decimals = 2
  ) |> 
  cols_label(
    term = "Term",
    estimate = "Estimate",
    std.error = "Std. Error",
    statistic = "t value",
    p.value = "p-value",
    conf.low = "95% CI (Low)",
    conf.high = "95% CI (High)"
  ) |> 
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels(everything())
  )
```

```{r}
library(ggplot2)
library(dplyr)

# Manually create the summary output as a tibble
avg_effect <- tibble(
  comparison = "Treated vs. Control",
  estimate = 1.55,
  std_error = 0.521,
  conf_low = 0.525,
  conf_high = 2.57
)

# Plot
ggplot(avg_effect, aes(x = comparison, y = estimate)) +
  geom_point(size = 4, color = "#2C3E50") +
  geom_errorbar(aes(ymin = conf_low, ymax = conf_high), width = 0.1, color = "#1ABC9C", linewidth = 1.2) +
  labs(
    title = "Effect of Exposure to Spanish Speakers on Attitude towards Immigration",
    subtitle = "Participants in the treatment group showed a significantly higher attitude score\ncompared to the control group (estimated increase = 1.55)",
    x = "",
    y = "Estimated Difference in att_end (Treated - Control)",
    caption = "Source: Enos Data"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold"),
    plot.subtitle = element_text(margin = margin(b = 10)),
    axis.text.x = element_text(face = "bold"),
    panel.grid.major.x = element_blank()
  )

```

Immigration is a highly contentious topic in American politics and is a key issue for many polititians. Using data from Enos which examines Boston commuters, some of whom were exposed to Spanish speakers on a train platform, we will attempt to answer the question "What is the average causal effect of exposure to Spanish-speakers on attitudes toward immigration?" One potential weakness in this approach is that the assumption of representativeness may not hold. I model the relationship between exposure to Spanish speakers and attitude towrds immigration, an integer between 3 and 15, with a linear model. The estimated causal effect was 1.55 with a 95% confidence interval between 0.51 and 2.88.
